\usepackage{hyperref}
\usepackage[hmargin=2cm,vmargin=2cm]{geometry}
\documentclass[margin,11pt]{resume}

\begin{document}
\begin{resume}

\vspace{30mm}

\section{\mysidestyle Awards \&\\ Achievements}

\begin{list2}
\item \textbf {All India Rank 77} in Joint Entrance Exam(JEE) conducted by Indian Institute of Technology among 5.5 lakhs candidates (\textbf{Top 0.01\%})
\item Selected for the Indian National Olympiads : \textbf{INPHO}(Physics), \textbf{INCHO}(Chemistry) conducted by HBCSE,  National \textbf{Top 1\%} in each of them
\item Accomplished \textbf {Ganit Pradnya State Level Mathematics Examination} conducted by Brihan Mumbai Ganit Adhyapak Mandal
\item Awarded \textbf {Institute Technical Special Mention}, 2013 for excellence in technical activities 
				
\vspace{-3mm}
\end{list2}\vspace{0.25mm}

\section{\mysidestyle Research Intern}
				\textbf{Visiting Scientist at  Technische University of Braunschweig, Germany\\} 				\emph{Guide: Prof. Dr. Sandor P. Fekete \& Prof. Dr. Alexander Kroller} \hfill {\textbf{2013}}\\
				Online Triangulation and Navigation Using a Swarm of Simple Robots. Contributed to practical aspects of real life problems involving minimizing overall error in navigation and localization, given minimum sensing capabilities

\vspace{-3mm}
\section{\mysidestyle Projects}

\textbf{AUVSI ROBOSUB, International Underwater Robotics Competition, San Deigo, California } \hfill \textbf{www.auv-iitb.org}
\vspace{1mm}\\ 
				Designing and developing a an unmanned autonomous underwater vehicle(AUV) 
				\textsl{Guide : Prof.Dr Hemandra Arya and Prof Leena Vachhani}\hfill \textbf{July 2012-ongoing}\\
				Currently working under the Software Subdivision:
				\begin{list2} 
				\item Finished \textbf{10\textsuperscript{th}} among 33 teams, at Robosub 2013
				\item Implementing Navigation using Markov Localization
				\end{list2}
				\vspace{-3mm}
\textbf{N-Body Simulation}\vspace{1mm} \hfill\\ 
				\textsl{Guide: Prof. Varsha Apte}\hfill \textbf{Autumn 2013}\\
				Designed an simulation which showed the interaction between different particles under the effect of intermolecular forces. The simulation involved using the famous \emph{Barnes-Hut Algorithm} to optimize on calculations \vspace{-2.75mm} 

\textbf{GIS Contour Plotting}\vspace{1mm} \hfill\\ 
				\textsl{Guide : Prof. Milind Sohoni and Prof. Adsul Bharat}	\hfill \textbf{May 2012}\\
				Plotted elevation and contours by obtaining sample data from \textbf{Google API's} using various kriging and interpolation techniques\vspace{-2.75mm} 

 
\section{\mysidestyle Positions of\\ Responsibility}

\begin{list2}
\item \textbf{Technical Mentor} \hfill\textbf{2013}: Mentored teams for technical summer projects under Student Technical Activity Body(STAB)
\end{list2}
\vspace{-3mm}
\section{\mysidestyle Extra\\Curricular\\Actvities}
\begin{list2}
\item Participated in  Hack U, conducted by Yahoo in 2013, designed a web-appilication for car-pooling services 
\item Completed the enduro3 night trek, 16kms long conducted by National Education Foundation
\end{list2}
\vspace{-3mm}
\section{\mysidestyle Key\\ Courses\\ Undertaken}

\textbf{Core} :
Operating Systems**, Compilers**, Artificial Intelligence**, 
Computer Architecture*, Databases*
Linear Optimization*, 
Design and Analysis of Algorithms, 
Discrete Structures, 
Automata Theory and Logic\\       
\textbf{Non-Core} : Linear Algebra, Numerical Analysis, Differential Equations\\
Note: The * marked courses will be completed by November 2013, ** marked courses will be completed by April 2014.
\vspace{-3mm}
\section{\mysidestyle Skills}
\begin{list2}
\item Programming Languages: C++/C, Prolog, Python, Plt Scheme, Java, Javascript,Php
\item Microcontroller: Intel 8085, AVR, PIC, Raspberry Pi, Arm-Cortex M4 and  FPGA's
\item Platforms: Linux, Robot Operating Systems(ROS)
\end{list2}	
\end{resume}
\end{document}
